Supplementary plots

### 2021-02-05 Manuscript/Manuscript_intro_methods_results.Rmd
updated data files after R update

Along the trajectory, we have to make sure that at a given stage (which implies that we are in a specific operating mode), our strategy is aligned with the goal that we have at this stage. At early stages, we want to find possibly working interventions. In statistical terms this means that we aim for a low Type II error. We do not want to miss effects. That means that our tests should be sensitive. This comes at the cost of specificity. We allow for false positives at this stage. 
Dirnagl (2016) [@dirnagl2016thomas]

*In exploratory mode, we allow for more false positives. This happens naturally, as we operate with low prior odds that our hypothesis is true.

* focus in exploration should rather be on proper descriptive statistics, including measures of variance and confidence intervals.

*

@@

\ \ \ \ In another approach, after conducting a two-sided two-sample *t*-test at the exploratory stage, we estimated the effect size and 95 percent CI around that estimate. We examined whether the CI covered our SESOI (0.5 and 1.0, respectively). If this was the case for an experiment, it advanced to the replication stage. Importantly, we did not consider the *p*-value additionally. Applying this decision criterion resulted in `r outcomes_all_distributions_init_samp_size_10$rep_attempts[6] / 100` and `r outcomes_all_distributions_init_samp_size_10$rep_attempts[5] / 100` percent of experiments moving to replication in case of the "optimistic" distribution and `r outcomes_all_distributions_init_samp_size_10$rep_attempts[2] / 100` and `r outcomes_all_distributions_init_samp_size_10$rep_attempts[1] / 100` percent for thes "pessimistic" distribution based on an SESOI of 0.5 and 1.0, respectively. Compared to the conventional significance threshold, the range of effect size estimates that proceeded to replication shifted and included less extreme values, and more values closer to zero. #figure?

@@

\ \ \ \ In our study, the pre-study odds were determined by the empirical effect size distributions and varied with the SESOI. In the "optimistic" scenario, the pre-study odds were `r round(outcomes_all_distributions_init_samp_size_10$prev_pop[6], 2)` and `r round(outcomes_all_distributions_init_samp_size_10$prev_pop[5], 2)` for SESOI of 0.5 and 1.0, respectively. In the "pessimistic" scenario pre-study odds were `r round(outcomes_all_distributions_init_samp_size_10$prev_pop[2], 2)` and `r round(outcomes_all_distributions_init_samp_size_10$prev_pop[1], 2)`, respectively. 
Across trajectory T1, the PPV drops below pre-study odds in both scenarios (Figure \@ref(fig:PPV)). After the within-lab replication study, the PPV is `r round(outcomes_all_distributions_init_samp_size_10$PPV_pop_prev[8], 2)` and  `r round(outcomes_all_distributions_init_samp_size_10$PPV_pop_prev[7], 2)` in the "optimitsic" scenario for SESOI of 0.5 and 1.0, respectively. In the "pessimistic" scenario, the PPV is `r round(outcomes_all_distributions_init_samp_size_10$PPV_pop_prev[4], 2)` and `r round(outcomes_all_distributions_init_samp_size_10$PPV_pop_prev[3], 2)`.
In trajectory T2, employing a SESOI at both stages along the decision-making process elevates the PPV above pre-study odds. Given our "optimistic" emoirical distribution, the PPV is `r round(outcomes_all_distributions_init_samp_size_10$PPV_pop_prev[6], 2)` and `r round(outcomes_all_distributions_init_samp_size_10$PPV_pop_prev[5], 2)` for SESOI of 0.5 and 1.0, respectively. In the "pessimistic" scenario, the PPV is `r round(outcomes_all_distributions_init_samp_size_10$PPV_pop_prev[2], 2)` and `r round(outcomes_all_distributions_init_samp_size_10$PPV_pop_prev[1], 2)`

>>>>

@@

\ \ \ \ In another approach, after conducting a two-sided two-sample *t*-test at the exploratory stage, we estimated the effect size and 95 percent CI around that estimate. We examined whether the CI covered our SESOI (0.5 and 1.0, respectively). If this was the case for an experiment, it advanced to the replication stage. Importantly, we did not consider the *p*-value additionally. Applying this decision criterion resulted in `r outcomes_all_distributions_init_samp_size_10$rep_attempts[6] / 100` and `r outcomes_all_distributions_init_samp_size_10$rep_attempts[5] / 100` percent of experiments moving to replication in case of the "optimistic" distribution and `r outcomes_all_distributions_init_samp_size_10$rep_attempts[2] / 100` and `r outcomes_all_distributions_init_samp_size_10$rep_attempts[1] / 100` percent for the "pessimistic" distribution based on an SESOI of 0.5 and 1.0, respectively. Compared to the conventional significance threshold, the range of effect size estimates that proceeded to replication shifted and included less extreme values, and more values closer to zero. #figure?

@@

\ \ \ \ In our study, the pre-study odds were determined by the empirical effect size distributions and varied with the SESOI. In the "optimistic" scenario, the pre-study odds were `r round(outcomes_all_distributions_init_samp_size_10$prev_pop[6], 2)` and `r round(outcomes_all_distributions_init_samp_size_10$prev_pop[5], 2)` for SESOI of 0.5 and 1.0, respectively. In the "pessimistic" scenario pre-study odds were `r round(outcomes_all_distributions_init_samp_size_10$prev_pop[2], 2)` and `r round(outcomes_all_distributions_init_samp_size_10$prev_pop[1], 2)`, respectively. 
Across trajectory T1, the PPV drops below pre-study odds in both scenarios (Figure \@ref(fig:PPV)). After the within-lab replication study, the PPV is `r round(outcomes_all_distributions_init_samp_size_10$PPV_pop_prev[8], 2)` and  `r round(outcomes_all_distributions_init_samp_size_10$PPV_pop_prev[7], 2)` in the "optimitsic" scenario for SESOI of 0.5 and 1.0, respectively. In the "pessimistic" scenario, the PPV is `r round(outcomes_all_distributions_init_samp_size_10$PPV_pop_prev[4], 2)` and `r round(outcomes_all_distributions_init_samp_size_10$PPV_pop_prev[3], 2)`.
In trajectory T2, employing a SESOI at both stages along the decision-making process elevates the PPV above pre-study odds. Given our "optimistic" emoirical distribution, the PPV is `r round(outcomes_all_distributions_init_samp_size_10$PPV_pop_prev[6], 2)` and `r round(outcomes_all_distributions_init_samp_size_10$PPV_pop_prev[5], 2)` for SESOI of 0.5 and 1.0, respectively. In the "pessimistic" scenario, the PPV is `r round(outcomes_all_distributions_init_samp_size_10$PPV_pop_prev[2], 2)` and `r round(outcomes_all_distributions_init_samp_size_10$PPV_pop_prev[1], 2)`.

### 2021-02-05 Manuscript/internal_revision/supplemetary_plots.Rmd
updated data files after R update

>>>>

```{r}
facet_names <- 
  c("equivalence.SESOI" = "SESOI within CI \nSESOI ",
    "significance.SESOI" = "Significance \nSESOI",
    "equivalence.standard" = "SESOI within CI \nStandard",
    "significance.standard" = "Significance \nStandard")

plot_PPV <- 
  ggplot(data = outcomes_10EU,
         aes(x = SESOI, y = PPV_pop_prev)) + 
  geom_point(size = 1.5) + 
  facet_wrap(~ trajectory, nrow = 2, ncol = 2,  labeller = labeller(.rows = facet_names)) + 
  labs(x = "SESOI", y = "Positive predictive value") +
  # scale_x_discrete(labels = c("SESOI within CI \nSESOI",
  #                             "Significance \nSESOI",
  #                             "SESOI within CI \nStandard",
  #                             "Significance \nStandard")) +
  scale_x_continuous(breaks = c(0.3, 0.5, 0.7, 1.0)) +
  theme_bw() +
  theme(axis.title.x = element_text(size = 11)) +
  theme(axis.title.y = element_text(size = 11)) +
  theme(axis.text.x = element_text(size = 7, colour = "black")) +
  theme(axis.text.y = element_text(size = 10, colour = "black")) +
  theme(strip.text.x = element_text(size = 11, colour = "black", face = "bold")) +
  theme(strip.text.y = element_text(size = 11, colour = "black", face = "bold")) +
  theme(strip.background = element_rect(fill = "white", color = "black"))

# hlines <- data.frame(pre_study_odds = c(outcomes_10EU$Prevalence[1], outcomes_10EU$Prevalence[5],
#                                         outcomes_10EU$Prevalence[9], outcomes_10EU$Prevalence[13]), 
#                      # distribution   = c(rep(plot_data$distribution[1], 2), 
#                      #                    rep(plot_data$distribution[5], 2)),
#                      SESOI          = rep(c("1", "0.7", "0.5", "0.3"))) 
# 
# 
# plot_PPV <- 
#   plot_PPV + 
#   geom_hline(data = hlines, 
#              aes(yintercept = pre_study_odds),
#              color = "red", lty = 2, size = .5)

```{r}
facet_names <- 
  c("equivalence.SESOI" = "SESOI within CI \nSESOI ",
    "significance.SESOI" = "Significance \nSESOI",
    "equivalence.standard" = "SESOI within CI \nStandard",
    "significance.standard" = "Significance \nStandard")

plot_FPR <- 
  ggplot(data = outcomes_10EU,
         aes(x = SESOI, y = FPR)) + 
  geom_point(size = 1.5) + 
  facet_wrap(~ trajectory, nrow = 2, ncol = 2,  labeller = labeller(.rows = facet_names)) + 
  labs(x = "SESOI", y = "False positive rate") +
  # scale_x_discrete(labels = c("SESOI within CI \nSESOI",
  #                             "Significance \nSESOI",
  #                             "SESOI within CI \nStandard",
  #                             "Significance \nStandard")) +
  scale_x_continuous(breaks = c(0.3, 0.5, 0.7, 1.0)) +
  theme_bw() +
  theme(axis.title.x = element_text(size = 11)) +
  theme(axis.title.y = element_text(size = 11)) +
  theme(axis.text.x = element_text(size = 7, colour = "black")) +
  theme(axis.text.y = element_text(size = 10, colour = "black")) +
  theme(strip.text.x = element_text(size = 11, colour = "black", face = "bold")) +
  theme(strip.text.y = element_text(size = 11, colour = "black", face = "bold")) +
  theme(strip.background = element_rect(fill = "white", color = "black"))

# hlines <- data.frame(pre_study_odds = c(outcomes_10EU$Prevalence[1], outcomes_10EU$Prevalence[5],
#                                         outcomes_10EU$Prevalence[9], outcomes_10EU$Prevalence[13]), 
#                      # distribution   = c(rep(plot_data$distribution[1], 2), 
#                      #                    rep(plot_data$distribution[5], 2)),
#                      SESOI          = rep(c("1", "0.7", "0.5", "0.3"))) 
# 
# 
# plot_PPV <- 
#   plot_PPV + 
#   geom_hline(data = hlines, 
#              aes(yintercept = pre_study_odds),
#              color = "red", lty = 2, size = .5)

plot_FPR
```
